Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-02-16 analysis/TAS_memo/memo_TAS_reviewers.Rmd

This memorandum replies to comments provided by the TAS associate editor and two reviewers. We believe the revised paper is much better as a result.

@@

@@

This comment is not clear to us. The real data analyses are based on real historical strike data from real criminal cases in the federal district court in Connecticut. If they wish, users of the app can run the model excluding any historical data (as this reviewer suggested) by not selecting the name of a prosecutor or defense attorney. Like our model, the app uses the $N(0,2)$ prior for the bias parameter. Similarly, the app user can alter the weight the historical strike data (if selected) by adjusting $\alpha$ (the power prior parameter). Thus, the app user can: (1) choose not to use historical data, (2) use historical data with equal weight as the current trial (alpha = 1), or (3) down-weight the historical trial data (alpha = 0.5 or alpha = 0.2). See also Item 1(6).

>>>>

This memorandum replies to comments provided by the TAS associate editor and two reviewers. We thank the editor and reviewers for their comments. We believe the revised paper is much better as a result.

@@

[editme]In any case, other authors analysing _Batson_ challallenge data have suggest other, more implicit forms of weighting cases based on trial-incompatibility. As we now mention in the paper [xx], @Gastwirth2014 suggests that trials with 'similar characteristics' be selected before conducting Cochran-Mantel-Haenszel tests. This is tantamount to setting the weight of incompatible cases to zero and compatible cases to 1. In such an instance, such weighing should be explicit and justified.

@@

This comment is not clear to us. The real data analyses are based on real historical strike data from real criminal cases in the federal district court in Connecticut. If they wish, users of the app can run the model excluding any historical data (as this reviewer suggested) by not selecting the name of a prosecutor or defense attorney. Like our model, the app uses the $N(0,2)$ prior for the bias parameter. Similarly, the app user can alter the weight of the historical strike data (if selected) by adjusting $\alpha$ (the power prior parameter). Thus, the app user can: (1) choose not to use historical data, (2) use historical data with equal weight as the current trial (alpha = 1), or (3) down-weight the historical trial data (alpha = 0.5 or alpha = 0.2). See also Item 1(6).
